Continuous developmental change can explain discontinuities in word learning

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

An unexpected outcome was that adult participants deviated slightly from the model's numbers. While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern. This deviation is interesting as it suggests that participants are more likely to pay attention and integrate additional sources of information when ambiguity is higher. \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}

@@

Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding varies.  We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (reducing the encoding uncertainty) in qualitatively similar representations across the life span.

The model made a new prediction to which we provided the first experimental test: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents. More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.  This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018]. That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features).

>>>>

An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern. This deviation is interesting as it suggests that participants are more likely to pay attention and integrate additional sources of information when ambiguity is higher. \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}

@@

Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model where perceptual stimuli are encoded probabilistically.  We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (i.e., uncertainty reduction) in qualitatively similar representations across the life span.

The model made a new prediction to which we provided the first experimental test: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents. More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.  This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018].

<!--That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features). -->

### 2019-01-31 cogsci/cogsci.tex
second version cogsci

Building on some previous discussions (e.g., Swingley, 2007; Yoshida et
al., 2009), we proposed a model which assumes that subtle perceptual
features are correctly encoded during word meaning learning, but that
the precision of this encoding varies. We tested the model's predictions
against data collected from preschool children and adults and we showed
that developmental changes in word-object mappings can indeed be
characterized as a continuous refinement (reducing the encoding
uncertainty) in qualitatively similar representations across the life
span.

The model made a new prediction to which we provided the first
experimental test: Learning similar words is not only modulated by the
similarity of their phonological forms, but also by the visual
similarity of their semantic referents. More generally, since visual
similarity is an early organizing feature in the semantic domain (e.g.,
Wojcik \& Saffran, 2013), our finding suggests that children may
prioritize the acquisition of words that are quite distant in the
semantic space. This suggestion is supported by recent findings based on
the investigation of early vocabulary growth (Engelthaler \& Hills,
2017; Sizemore, Karuza, Giusti, \& Bassett, 2018). That said, further
work is needed to explore the effect on word learning of other semantic
dimensions that could be encoded by children (e.g.,
conceptual/functional features).

>>>>

Building on some previous discussions (e.g., Swingley, 2007; Yoshida et
al., 2009), we proposed a model where perceptual stimuli are encoded
probabilistically. We tested the model's predictions against data
collected from preschool children and adults and we showed that
developmental changes in word-object mappings can indeed be
characterized as a continuous refinement (i.e., uncertainty reduction)
in qualitatively similar representations across the life span.

The model made a new prediction to which we provided the first
experimental test: Learning similar words is not only modulated by the
similarity of their phonological forms, but also by the visual
similarity of their semantic referents. More generally, since visual
similarity is an early organizing feature in the semantic domain (e.g.,
Wojcik \& Saffran, 2013), our finding suggests that children may
prioritize the acquisition of words that are quite distant in the
semantic space. This suggestion is supported by recent findings based on
the investigation of early vocabulary growth (Engelthaler \& Hills,
2017; Sizemore, Karuza, Giusti, \& Bassett, 2018).
